---
title: "COVID-19 Trends by UCI Statistics"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---
<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
</style>

#### Use <span style="color:#FFF; background-color: #0064A4">CA County Trends</span> dropdown menu for other county comparisons and <span style="color:#FFF; background-color: #0064A4">OC Maps</span> dropdown menu for maps of Orange County, CA. Also, check out [OC COVID-19 Situation Report](https://www.stat.uci.edu/oc_covid_model/index.html) for modeling and forecasting of COVID-19 dynamics in Orange County, CA.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, fig.retina = 2)
```

```{r get_plots}
source("code/functions.R")
counties_of_interest <- c("San Diego",  "Los Angeles",  "Orange", "Alameda", "Santa Clara")
plots <- get_county_plots(counties_of_interest)
```

<div class = "row">
<div class = "col-md-6">
```{r hospitalizations_plot}
watermark(plots$hospitalizations_plot)
```
</div>
<div class = "col-md-6">
```{r icu_plot}
watermark(plots$icu_plot)
```
</div>
</div>
<div class = "row">
<div class = "col-md-6">
```{r cases_plot}
watermark(plots$cases_plot)
```
</div>
<div class = "col-md-6">
```{r deaths_plot}
watermark(plots$deaths_plot)
```
</div>
</div>
Note that if deaths have been incorrectly reported in the past, current counts will be artificially decreased to account for the error. This may lead to negative deaths being reported. 

Data collected from the [California Open Data Portal](https://data.ca.gov/group/covid-19).

Last updated on `r Sys.Date()`. 

Last available date in the [California Open Data Portal](https://data.ca.gov/group/covid-19) is `r as.Date(plots$data_date)`.

